A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-10-07 Simulator/article.tex
la2pdf commit - 2015:10:07	11:23:21	(Wed 7.Oct)

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    bookmarksnumbered ]{hyperref}

\else
   \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
   \usepackage{breakurl}                        % Allows 'dvips' driver to break links
\fi

>>>>

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
% \ifCLASSINFOpdf
% %    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
%    \usepackage[pdftex,
%     final,                %Keep hyperlink stuff even when in draft mode
%     breaklinks=true,      %Break links when necessary
%     linktocpage=true,     %Enable link to page?
%     linkcolor=black,  %Colour of links to labels within document
%     citecolor=black,      %Colour of links to the biliography
%     filecolor=red,        %Colour of links to local files
%     pagecolor=black,        %Colour of links to other pages withing document
%     urlcolor=Blue,        %Colour of the links to external URLs
%     colorlinks=true,      %??
%     plainpages=false,     %Store roman/arabic numbering differently to avoid
%     bookmarksnumbered ]{hyperref}
% 
% \else
%    \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
%    \usepackage{breakurl}                        % Allows 'dvips' driver to break links
% \fi
